The \dealii Library, Version 9.5

### 2023-06-22 9.5/paper.tex
Add myself to the list of authors
minor rewriting of the PETSc section

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Marc Fehling,
    Marco Feder,
    Johannes Heinz,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells
  },
  pdftitle={The deal.II Library, Version 9.5, 2023},
}

@@

@@

The \dealii classes wrapping \petsc objects have been heavily rewritten
to support the nonlinear solver \snes and the Ordinary Differential Equations (ODE)
solver \ts \cite{abhyankar2018petsc}.
First, we briefly describe the most important improvements to the existing
classes and then outline the newly designed interfaces to the nonlinear solvers, together
with a new interface to the communication module \petscsf in \petsc \cite{zhang2021petscsf}.

@@

We refer interested readers to our documentation for other more advanced
functions of the \ts and \snes wrappers, and to the {\tt tests/petsc/} folder
for examples on how to use them.

We close this section by introducing the interface to the \petscsf class,
the abstract communication model of \petsc. The \dealii interface to
\petscsf has been modelled on those of \texttt{Utilities::MPI::Partitioner} and
\texttt{Utilities::MPI::NoncontiguousPartitioner}. Future developments
will add support for GPU buffers.

>>>>

\hypersetup{
  pdfauthor={
    Daniel Arndt,
    Wolfgang Bangerth,
    Maximilian Bergbauer,
    Marc Fehling,
    Marco Feder,
    Johannes Heinz,
    Timo Heister,
    Luca Heltai,
    Martin Kronbichler,
    Matthias Maier,
    Peter Munch,
    Jean-Paul Pelteret,
    Bruno Turcksin,
    David Wells,
    Stefano Zampini
  },
  pdftitle={The deal.II Library, Version 9.5, 2023},
}

@@

\author[13]{Stefano Zampini}
\affil[13]{Extreme Computing Research Center, King Abdullah University of Science and Technology,
  23955-6900 Thuwal, Saudi Arabia.
  {\texttt{stefano.zampini@gmail.com}}}

@@

The \dealii classes wrapping \petsc objects have been heavily rewritten
to support the System of Nonlinear Equations Solver \snes and the Ordinary Differential Equations (ODE)
solver \ts \cite{abhyankar2018petsc}.
First, we briefly describe the most important improvements to the existing
classes and then outline the newly designed interfaces to the nonlinear solvers, together
with a new interface to the communication module \petscsf in \petsc \cite{zhang2021petscsf}.

@@

We close this section by introducing the interface to the \petscsf class,
the abstract communication model of \petsc. The \dealii interface to
\petscsf has been modelled on \texttt{Utilities::MPI::Partitioner} and
\texttt{Utilities::MPI::NoncontiguousPartitioner}, with minimal changes for the
communication routines API; the equivalent classes based
on \petscsf are \texttt{PETScWrappers::Partitioner} and
\texttt{PETScWrappers::CommunicationPattern}.
Future developments will add support for GPU buffers.

We refer interested readers to our documentation for other more advanced
functions of the \snes, \ts and \petscsf wrappers, and to the {\tt tests/petsc/} folder
for examples on how to use them.
